### 2019-04-19 Writing/supplementary/Sup1-CharDiff.tex
Updated char diff demo

\begin{equation}
    CD_{(x,y)} = 1 - 2\left(\abs*{\frac{\sum_{i}^{n}\abs{x_{i} - y_{i}}}{n}-\frac{1}{2}}\right)
\end{equation}

@@

For any $n \in [1;\infty)$ and $x_{n}$ and $y_{n} \in (0,1)$ because the difference between character states is considered as Fitch-like (unordered; i.e. the difference between two different characters states is equal to $1$ and the difference between two identical character states is equal to $0$):

\begin{equation}
    \label{positive_demo}
    \begin{gathered}
    0 \leq  \abs{x_{n}-y_{n}} \leq 1\\
    0 \leq  \sum_{i=1}^{n}\abs{x_{i}-y_{i}} \leq n\\
    0 \leq  \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n} \leq 1\\
    0 \leq  \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} \leq \frac{1}{2}\\
    0 \leq  2\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} \leq 1\\
    0 \leq  1 - 2\left(\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}\right) \leq 1\\
    \end{gathered}
\end{equation}

@@

For any $n \in [1;\infty)$ and $x_{n} = y_{n}$ then:
%TG: Is that valid for a demonstration?
\begin{equation}
    \label{identitydemo}
    \begin{aligned}
    \abs{x_{n}-y_{n}} &= 0\\
    \sum_{i}^{n}\abs{x_{i}-y_{i}} &= 0\\
    \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n} &= 0\\
    \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} &= \frac{1}{2}\\
    2\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} &= 1\\
    1 - 2\left(\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}\right) &= 0\\
    \end{aligned}
\end{equation}

@@

\begin{equation}
    \label{equality_demo}
    \begin{aligned}
    \abs{x_{n}-y_{n}} &= \abs{y_{n}-x_{n}}\\
    \sum_{i}^{n}\abs{x_{i}-y_{i}} &= \sum_{i}^{n}\abs{y_{i}-x_{i}}\\
    \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n} &= \frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}\\
    \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} &= \abs*{\frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}-\frac{1}{2}}\\
    2\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} &= 2\abs*{\frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}-\frac{1}{2}}\\
    1 - 2\left(\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}\right) &= 1 - 2\left(\abs*{\frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n}-\frac{1}{2}}\right)\\
    \end{aligned}
\end{equation}

@@

For any $n, j, b \in [1;\infty)$ and $x_{n}$, $y_{j}$, $z_{b}$ $\in (0,1)$:

\begin{equation}
    \label{subadditivity_demo}
    \begin{aligned}
    CD_{x,y} &\leq CD_{x,z} + CD_{z,y}\\
    \text{if:}\\
     1 - 2\left(\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}\right)
     &\leq 
     1 - 2\left(\abs*{\frac{\sum_{k}^{j}\abs{x_{k}-z_{k}}}{j}-\frac{1}{2}}\right) 
     +
     1 - 2\left(\abs*{\frac{\sum_{a}^{b}\abs{z_{a}-y_{a}}}{b}-\frac{1}{2}}\right) \\
     \text{then, the opposite is:}\\
     \underbrace{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} }_{\in[0,1/2]}
     &\geq 
     \underbrace{\abs*{\frac{\sum_{k}^{j}\abs{x_{k}-z_{k}}}{j}-\frac{1}{2}} }_{\in[0,1/2]}
     +
     \underbrace{\abs*{\frac{\sum_{a}^{b}\abs{z_{a}-y_{a}}}{b}-\frac{1}{2}} }_{\in[0,1/2]} - 2\\
     \text{thus:}\\
     \in[0,\frac{1}{2}] &\geq \in[0,\frac{1}{2}] + \in[0,\frac{1}{2}] -2 \\
     \in[0,\frac{1}{2}] &\geq \in[-2,-1]\\
    \end{aligned}
\end{equation}

Thus equation \ref{Subadditivity} is true.

>>>>

\begin{equation}
    CD_{(x,y)} = \frac{\sum_{i}^{n}\abs{x_{i} - y_{i}}}{n-1}
\end{equation}

@@

For any $n \in [1;\infty)$ and $x_{n}$ and $y_{n} \in (0,1)$ because the difference between character states is considered as Fitch-like (unordered; i.e. the difference between two different characters states is equal to $1$ and the difference between two identical character states is equal to $0$).
Furthermore, following the $xyz$ notation described above, for any $n > 1$, $x_{1}-y_{1}=0$.
Therefore the sum of the differences $\sum_{i=1}^{n}\abs{x_{i}-y_{i}} \in [0;(n-1)]$.

\begin{equation}
    \label{positive_demo}
    \begin{gathered}
    0 \leq  \abs{x_{n}-y_{n}} \leq 1\\
    0 \leq  \sum_{i=1}^{n}\abs{x_{i}-y_{i}} \leq (n-1)\\
    0 \leq  \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n-1} \leq 1\\
    \end{gathered}
\end{equation}

@@

For any $n \in [1;\infty)$ and $x_{n} = y_{n}$ then:
%TG: Is that valid for a demonstration?
\begin{equation}
    \label{identitydemo}
    \begin{aligned}
    \abs{x_{n}-y_{n}} &= 0\\
    \sum_{i}^{n}\abs{x_{i}-y_{i}} &= 0\\
    \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n-1} &= 0\\
    \end{aligned}
\end{equation}

@@

\begin{equation}
    \label{equality_demo}
    \begin{aligned}
    \abs{x_{n}-y_{n}} &= \abs{y_{n}-x_{n}}\\
    \sum_{i}^{n}\abs{x_{i}-y_{i}} &= \sum_{i}^{n}\abs{y_{i}-x_{i}}\\
    \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n-1} &= \frac{\sum_{i}^{n}\abs{y_{i}-x_{i}}}{n-1}\\
    \end{aligned}
\end{equation}

@@

For any $n, \in [1;\infty)$ and $x_{n}$, $y_{n}$, $z_{n}$ $\in (0,1)$:

\begin{equation}
    \label{equality_demo}
    \begin{aligned}
    \text{since:}\\
    \underbrace{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n-1}}_{\in[0,1]}
    &\leq
    \underbrace{\frac{\sum_{i}^{n}\abs{x_{i}-z_{i}}}{n-1}}_{\in[0,1]}
    +
    \underbrace{\frac{\sum_{i}^{n}\abs{z_{i}-y_{i}}}{n-1}}_{\in[0,1]}\\
    \text{thus:}\\
    \in[0,1] &\leq \in[0,1] + \in[0,1] \\
    \in[0,1] &\leq \in[0,2]\\
    \end{aligned}
\end{equation}
Thus equation \ref{Subadditivity} is true.
